---
title: "Lab 07 - Modelling course evaluations"
author: [TEAM NAME]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
evals %>%
  ggplot() +
  geom_histogram(mapping = aes(x = score, binwidth = 20))

```

The above visualization shows that the data is right-skewed with students generally giving higher scores, with a peak between 4 and 5.

### Exercise 2

```{r viz-score-bty, eval = FALSE}
# add the code for each plot and assign them to the names as outlined below
# remove eval = FALSE from the code chunk options
# knit the document, and you'll see them appear next to each other
# this uses the patchwork package loaded above
# learn more about patchwork at https://patchwork.data-imaginist.com/
# it might be useful for your presentations!
plot_geom_point  <- ggplot(data = evals) +
  geom_point(mapping = aes(x = bty_avg, y = score))

plot_geom_jitter <- ggplot(data = evals) +
  geom_jitter(mapping = aes(x = bty_avg, y = score))

plot_geom_point + plot_geom_jitter
```

Jitter adds a small amount of random variation to each point, which allows points that would be stacked on top of each other to be seen individually. In the intial plot, many points were stacked, leading the viewer to believe there were fewer points at that location than there really were. 

### Exercise 3

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

score = 0.0666 * bty_avg + 3.88

### Exercise 4

```{r viz-score_bty_fit}
ggplot(data = evals, mapping = aes(x = bty_avg, y = score)) +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE, formula = "y ~ x", colour = "Orange")

```

### Exercise 5

*Add interpretation of intercept here.*

### Exercise 6

*Add interpretation of intercept here.*

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
